---
title: "Heuckeroth-Wolfson Mechanobiology V4"
subtitle: "Identifying the NicheNet data sources for ligand-receptor and ligand-target interactions"
author: Katherine Beigel
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
---

This can be run after `Up_in_Unstretched/scripts/LR_NicheNet_Analysis_unloadedUP_V4.Rmd` to identify the model data sources for the interaction preidcted by NicheNet.

```{r Packages}
# Utility
library(tidyverse)

# Analysis
library(nichenetr)
library(OmnipathR)
```


```{r Project information}
proj = "unloaded"
proj_long = "Up_in_Unstretched"

# For Unstretched, we reported the top 1 to 10 ligands.
top_gene_lab = 'Top1to10'

version = "V4"
```

# Define a table of **ligand-receptor interactions of interest** that we want to get evidence for
```{r Interactions to find evidence for}
interactions_oi = read_tsv(
    file = paste0(
    proj_long, "/sankey_inferredLT/",
    proj_long, "_", "Top1to10", "-ligands-byLog2FC_",
    "all", "-LRlinks_", "all", "-LTlinks_Table_InferredLTPaths_", version, ".csv")
)
```


# Load in the modified model (after generating these files from `Up_in_Unstretched/scripts/LR_NicheNet_Analysis_unloadedUP_V4.Rmd`)

## Data sources in the NicheNet prior model

There are two main parts of how ligand-receptor interactions are defined in the NicheNet model: the ligand-receptor network (`lr_network`), which is used to screen the data for LR interactions, and the signaling network (`sig_network`) which is used to construct the weights for the ligand-receptor interactions.

The `lr_network` basically only has two databases/sources: `omnipath` (https://omnipathdb.org/) and `nichenet_verschueren` (interactions described here in this paper: https://pubmed.ncbi.nlm.nih.gov/32589946/; more info in the preprint for the updated NicheNet model: https://www.biorxiv.org/content/10.1101/2023.06.13.544751v1 )

The `sig_network` has additional databases and sources which may provide additional support for certain interactions, so we will look at that as well.

```{r Load in modified model}

nnetdata_dir = "data/"

lr_network = readRDS(paste0(nnetdata_dir, "nichenet_prior_model_V2_modified/", "lr_network_modified_", version, ".rds"))
sig_network = readRDS(paste0(nnetdata_dir, "nichenet_prior_model_V2_modified/", "sig_network_modified_", version, ".rds"))
gr_network = readRDS(paste0(nnetdata_dir, "nichenet_prior_model_V2_modified/", "gr_network_modified_", version, ".rds"))

weighted_networks = readRDS(paste0(nnetdata_dir, "nichenet_prior_model_V2_modified/", "weighted_networks_modified_", version, ".rds"))
ligand_target_matrix = readRDS(file = paste0(nnetdata_dir, "nichenet_prior_model_V2_modified/", "ligand_target_matrix_modified_", version, ".rds"))
ligand_tf_matrix = readRDS(file = paste0(nnetdata_dir, "nichenet_prior_model_V2_modified/", "ligand_tf_matrix_modified_", version, ".rds"))

weighted_networks_lr = weighted_networks$lr_sig %>%
  # inner_join only keep observations from x that have a matching key in y, distinct keeps only unique rows
  inner_join(lr_network %>% distinct(from, to), by = c("from", "to")) # interactions and their weights in the ligand-receptor + signaling network

```


# ################################ !!!!!!!!!!!!!!!!!!!! CODE FROM NICHENET BELOW !!!!!!!!!!!!!!!!!!!! ################################################

# ####################################################################################################################################################
# ####################################################################################################################################################
# ####################################################################################################################################################
# THIS CODE COMES FROM NICHENET -- WE NEED TO USE THIS TO PRODUCE THE ORIGINAL TABLE FOR THE LR_NETWORK THAT CONTAINS THE SOURCES

This following block of code is pulled from the NicheNet model v2 construction scripts from the NicheNet authors, from Zenodo record: https://zenodo.org/records/8016880 
- Code in the following chunk is from the file: `NicheNet_V2/networks/scripts/ligand_receptor/3-make_new_LR_network_omnipath.R` at https://zenodo.org/records/8016880

I have made on modification in this code, which is how `lr_network_nichenet` is defined (I want to use my version of the lr_network)

```{r NicheNet_V2/networks/scripts/ligand_receptor/3-make_new_LR_network_omnipath.R}

######################################################################################################################################################

### Strategy: focus on the bona fide ligands and receptors etc; step 2 and then look in the Omnipath interaction collection whether we can find links between those

######################################################################################################################################################


######################################################################################################################################################

### Step 0: Define functions that will be used later on

######################################################################################################################################################


mutate_cond <- function(.data, condition, ..., envir = parent.frame()) {
  condition <- eval(substitute(condition), .data, envir)
  .data[condition, ] <- .data[condition, ] %>% mutate(...)
  .data
}

get_ligands_receptors_annotations = function(all_annotations){
  ############  start by getting all intercellular communication annotations ############  
  
  ############ define ligands and receivers, aka transmitters and receivers in omnipath language  ############  
  
  all_ligands = all_annotations %>% filter(transmitter == TRUE & entity_type != "complex") %>% pull(genesymbol) %>% unique()
  all_receptors = all_annotations %>% filter(receiver == TRUE & entity_type != "complex") %>% pull(genesymbol) %>% unique()
  
  #### define orphan ligands: #### 
  ## orphan ligands: secreted proteins that are not receivers, but are not annotated as transmitter
  ## often case if some data sources don't include them in that way, like NAMPT in ConnectomeDB 2020
  ## to be sure they are secreted: filter out proteins that are more more likely to be intracellular than secreted
  intracellular_ligands_receptors = all_annotations %>% filter(aspect == "locational") %>% group_by(genesymbol) %>% top_n(1, consensus_score) %>% filter(parent == "intracellular") %>% pull(genesymbol) %>% unique()
  orphan_ligands = all_annotations %>% filter(secreted == TRUE & entity_type != "complex") %>% pull(genesymbol) %>% 
    setdiff(intracellular_ligands_receptors) %>% sort() %>% 
    setdiff(all_annotations %>% filter(transmitter == TRUE & entity_type != "complex") %>% pull(genesymbol))
  
  ######## filter out transmitters that are more likely to be receivers -- and vice versa -- ######## 
  ## start by defining bona fide transmitters and receivers, and proteins that can be both
  
  transmitter_only = all_annotations %>% filter(transmitter == TRUE & entity_type != "complex") %>% pull(genesymbol) %>% setdiff(
    all_annotations %>% filter(receiver == TRUE & entity_type != "complex") %>% pull(genesymbol)
  ) %>% unique() ## note: these are not all trustworthy!!
  
  receiver_only = all_annotations %>% filter(receiver == TRUE & entity_type != "complex") %>% pull(genesymbol) %>% setdiff(
    all_annotations %>% filter(transmitter == TRUE & entity_type != "complex") %>% pull(genesymbol)
  ) %>% unique()
  
  transmitter_receiver = all_annotations %>% filter(receiver == TRUE & entity_type != "complex") %>% pull(genesymbol) %>% intersect(
    all_annotations %>% filter(transmitter == TRUE & entity_type != "complex") %>% pull(genesymbol)
  ) %>% unique()
  
  # determine now the consensus score of each protein to be transmitter, receiver, or both
  transmitter_receiver_df_score_transmitter = all_annotations %>% filter(genesymbol %in% transmitter_receiver) %>% distinct(genesymbol, transmitter, receiver, consensus_score) %>% filter(transmitter == TRUE & receiver == FALSE) %>% group_by(genesymbol) %>% top_n(1, consensus_score) %>% select(genesymbol, consensus_score) %>% rename(consensus_score_transmitter = consensus_score) %>% ungroup()
  transmitter_receiver_df_score_receiver = all_annotations %>% filter(genesymbol %in% transmitter_receiver) %>% distinct(genesymbol, transmitter, receiver, consensus_score) %>% filter(transmitter == FALSE & receiver == TRUE) %>% group_by(genesymbol) %>% top_n(1, consensus_score) %>% select(genesymbol, consensus_score) %>% rename(consensus_score_receiver = consensus_score) %>% ungroup()
  transmitter_receiver_df_score_transmitter_receiver = all_annotations %>% filter(genesymbol %in% transmitter_receiver) %>% distinct(genesymbol, transmitter, receiver, consensus_score) %>% filter(transmitter == TRUE & receiver == TRUE) %>% group_by(genesymbol) %>% top_n(1, consensus_score) %>% select(genesymbol, consensus_score) %>% rename(consensus_score_transmitter_receiver = consensus_score) %>% ungroup()
  
  transmitter_receiver_df = transmitter_receiver_df_score_transmitter %>% full_join(transmitter_receiver_df_score_receiver) %>% full_join(transmitter_receiver_df_score_transmitter_receiver)
  
  transmitter_receiver_df = transmitter_receiver_df %>% 
    mutate_cond(is.na(consensus_score_transmitter), consensus_score_transmitter = 0) %>% 
    mutate_cond(is.na(consensus_score_receiver), consensus_score_receiver = 0) %>% 
    mutate_cond(is.na(consensus_score_transmitter_receiver), consensus_score_transmitter_receiver = 0)
  transmitter_receiver_df = transmitter_receiver_df %>% drop_na() %>% filter(consensus_score_transmitter > 0 | consensus_score_receiver > 0 |  consensus_score_transmitter_receiver > 0)
  
  # filter out proteins that are more likely transmitter than other
  transmitter_only_2 = transmitter_receiver_df %>% filter(consensus_score_transmitter > (consensus_score_receiver + 1) & consensus_score_transmitter > (consensus_score_transmitter_receiver + 1) ) %>% pull(genesymbol)
  
  # filter out proteins that are more likely receiver than other
  receiver_only_2 = transmitter_receiver_df %>% filter(consensus_score_receiver > (consensus_score_transmitter + 1) & consensus_score_receiver > (consensus_score_transmitter_receiver + 1) )  %>% pull(genesymbol)
  
  # filter out proteins that are more likely both transmitter and receiver 
  transmitter_receiver_2 = transmitter_receiver_df %>% filter(! genesymbol %in% union(transmitter_only_2, receiver_only_2)) %>% pull(genesymbol)
  
  ####### now get list of potential ligands and receptors based on the previous analyses ####### 
  
  possible_ligands = c(transmitter_only, transmitter_only_2, transmitter_receiver_2, orphan_ligands) %>% unique()
  possible_receptors = c(receiver_only, receiver_only_2, transmitter_receiver_2) %>% unique()
  return(list(ligands = possible_ligands, receptors = possible_receptors) )
}

get_ligands_receptors_ligrec = function(ligrec){
  # filter out the complexes
  ligrec = ligrec %>% filter(!(entity_type_intercell_source == "complex" |
                                 entity_type_intercell_target == "complex"))
  ligrec_filtered = ligrec %>% filter(sources != "Wang") %>% 
    filter(category_intercell_source %in% c("ligand","cell_adhesion","cell_surface_ligand", "secreted","interleukins_hgnc", "chemokine_ligands_hgnc", "endogenous_ligands_hgnc","surface_ligand", "secreted_enzyme") & category_intercell_target %in% c("receptor","cell_adhesion","interleukin_receptors_hgnc")) 
  
  ligrec_filtered = ligrec_filtered %>% filter(!database_intercell_source %in% c("Omnipath","LRdb;OmniPath","GO_Intercell;OmniPath","scConnect;OmniPath","Cellinker;OmniPath","Cellinker;scConnect;OmniPath","Cellinker;Zhong2015;OmniPath") & !database_intercell_target %in% c("Omnipath","LRdb;OmniPath","GO_Intercell;OmniPath","scConnect;OmniPath","Cellinker;OmniPath","Cellinker;scConnect;OmniPath","Cellinker;Zhong2015;OmniPath"))
  
  trustworthy_sources_a = ligrec_filtered  %>%
    filter(consensus_score_intercell_source > 1) %>% pull(source_genesymbol) %>% unique()
  
  trustworthy_targets_a = ligrec_filtered %>% 
    filter(consensus_score_intercell_target > 1) %>% pull(target_genesymbol) %>% unique()
  
  # are there ligands/receptors that have only a score of <= 2 for one rol, but 0/1 for the other role?
  source_df = ligrec_filtered %>% 
    select(source_genesymbol, consensus_score_intercell_source) %>% rename(gene = source_genesymbol, score_source = consensus_score_intercell_source)
  target_df = ligrec_filtered %>% 
    select(target_genesymbol, consensus_score_intercell_target) %>% rename(gene = target_genesymbol, score_target = consensus_score_intercell_target)
  
  gene_df = source_df %>% full_join(target_df) %>% mutate_cond(is.na(score_source), score_source = 0) %>% mutate_cond(is.na(score_target), score_target = 0) %>% mutate(diff = score_source - score_target, summation = score_source + score_target) %>% distinct() # inner join maybe not ideal -- some lgiands and receptors were unique ligands and receptors
  gene_df = gene_df %>% group_by(gene) %>% top_n(1, summation) %>% distinct() %>% ungroup() ## this was a crucial thing!
  
  dubious_sources_targets = gene_df  %>% filter(score_source == score_target) %>% pull(gene) %>% unique() %>% sort()
  
  dubious_sources = gene_df %>% filter(diff == 1) %>% pull(gene) %>% setdiff(trustworthy_sources_a) %>% sort()
  dubious_targets = gene_df %>% filter(diff == -1) %>% pull(gene) %>% setdiff(trustworthy_targets_a) %>% sort()
  
  # far from perfect now, but at least we have something useful and filtered out the biggest shit
  ligrec_filtered = ligrec_filtered %>% filter(source_genesymbol %in% c(trustworthy_sources_a, dubious_sources_targets, dubious_sources) & target_genesymbol %in% c(trustworthy_targets_a, dubious_sources_targets, dubious_targets))
  
  possible_ligands = c(trustworthy_sources_a, dubious_sources_targets, dubious_sources) %>% unique()
  possible_receptors = c(trustworthy_targets_a, dubious_sources_targets, dubious_targets) %>% unique()
  
  return(list(ligands = possible_ligands, receptors = possible_receptors) )
  
}

## test function to demonstrate we really have to include these filters
get_ligands_receptors_ligrec_bad = function(ligrec){
  # filter out the complexes
  ligrec = ligrec %>% filter(!(entity_type_intercell_source == "complex" |
                                 entity_type_intercell_target == "complex"))
  ligrec_filtered = ligrec %>% 
    filter(category_intercell_source %in% c("ligand","cell_adhesion","cell_surface_ligand", "secreted","interleukins_hgnc", "chemokine_ligands_hgnc", "endogenous_ligands_hgnc","surface_ligand", "secreted_enzyme") & category_intercell_target %in% c("receptor","cell_adhesion","interleukin_receptors_hgnc")) 
  
  trustworthy_sources_a = ligrec_filtered  %>%
    filter(consensus_score_intercell_source > 1) %>% pull(source_genesymbol) %>% unique()
  
  trustworthy_targets_a = ligrec_filtered %>% 
    filter(consensus_score_intercell_target > 1) %>% pull(target_genesymbol) %>% unique()
  
  # are there ligands/receptors that have only a score of <= 2 for one rol, but 0/1 for the other role?
  source_df = ligrec_filtered %>% 
    select(source_genesymbol, consensus_score_intercell_source) %>% rename(gene = source_genesymbol, score_source = consensus_score_intercell_source)
  target_df = ligrec_filtered %>% 
    select(target_genesymbol, consensus_score_intercell_target) %>% rename(gene = target_genesymbol, score_target = consensus_score_intercell_target)
  
  gene_df = source_df %>% full_join(target_df) %>% mutate_cond(is.na(score_source), score_source = 0) %>% mutate_cond(is.na(score_target), score_target = 0) %>% mutate(diff = score_source - score_target, summation = score_source + score_target) %>% distinct() # inner join maybe not ideal -- some lgiands and receptors were unique ligands and receptors
  gene_df = gene_df %>% group_by(gene) %>% top_n(1, summation) %>% distinct() %>% ungroup() ## this was a crucial thing!
  
  dubious_sources_targets = gene_df  %>% filter(score_source == score_target) %>% pull(gene) %>% unique() %>% sort()
  
  dubious_sources = gene_df %>% filter(diff == 1) %>% pull(gene) %>% setdiff(trustworthy_sources_a) %>% sort()
  dubious_targets = gene_df %>% filter(diff == -1) %>% pull(gene) %>% setdiff(trustworthy_targets_a) %>% sort()
  
  # far from perfect now, but at least we have something useful and filtered out the biggest shit
  ligrec_filtered = ligrec_filtered %>% filter(source_genesymbol %in% c(trustworthy_sources_a, dubious_sources_targets, dubious_sources) & target_genesymbol %in% c(trustworthy_targets_a, dubious_sources_targets, dubious_targets))
  
  possible_ligands = c(trustworthy_sources_a, dubious_sources_targets, dubious_sources) %>% unique()
  possible_receptors = c(trustworthy_targets_a, dubious_sources_targets, dubious_targets) %>% unique()
  
  return(list(ligands = possible_ligands, receptors = possible_receptors) )
  
}

######################################################################################################################################################

### Step 1: Get confident ligand and receptor annotations

######################################################################################################################################################


### step 1A: get ligands and receptors based on annotations in the Intercell Database of Omnipath
all_annotations = import_omnipath_intercell()
ligands_receptors_test = get_ligands_receptors_annotations(all_annotations) 

## some bad receiver-transmitter annotations -- therefore filter out
all_annotations = all_annotations %>% setdiff(
  all_annotations %>% filter(aspect == "functional" & database %in% c("GO_Intercell","OmniPath")) 
)
ligands_receptors_1 = get_ligands_receptors_annotations(all_annotations) # much better

# check which bad ligands and receptors we removed now
ligands_receptors_test$ligands %>% setdiff(ligands_receptors_1$ligands) %>% sort() # TRAF4, ACTA1, CDK4, CCND1
ligands_receptors_test$receptors %>% setdiff(ligands_receptors_1$receptors) %>% sort() # C3 and CCND1

### step 1B: get ligands and receptors based on interactions in the Omnipath LR network
omnipath_broad = OmnipathR::import_intercell_network(omnipath = TRUE, ligrecextra = TRUE)
ligands_receptors_2 = get_ligands_receptors_ligrec(omnipath_broad)
ligands_receptors_bad = get_ligands_receptors_ligrec_bad(omnipath_broad)

possible_ligands = union(ligands_receptors_1$ligands, ligands_receptors_2$ligands)
possible_receptors = union(ligands_receptors_1$receptors, ligands_receptors_1$receptors)

# check which ligands/receptors would be missed if not including both
ligands_receptors_2$ligands %>% setdiff(ligands_receptors_1$ligands) %>% sort() # BTLA, CD226, CD80, CD86, CXCL16, DPP4, EPHA4, IFNA13, PVR
ligands_receptors_1$ligands %>% setdiff(ligands_receptors_2$ligands) %>% sort() # IFNA1, FN1, 

ligands_receptors_2$receptors %>% setdiff(ligands_receptors_1$receptors) %>% sort() # ICAM1, VCAM1
ligands_receptors_1$receptors %>% setdiff(ligands_receptors_2$receptors) %>% sort() # C3AR1

ligands_receptors_bad$ligands %>% setdiff(ligands_receptors_2$ligands) %>% sort() #JAK2, NOTCH1, PIK3CA, TP53
ligands_receptors_bad$receptors %>% setdiff(ligands_receptors_2$receptors) %>% sort() # JAK2, CX3CL1, CXCL16

### step1C: filter out transmitters that are more likely to be intracellular than extracellular than plasma membrane
# get intracellular ligands

intracellular_score_df = all_annotations %>% filter(genesymbol %in% c(possible_ligands, possible_receptors) & aspect == "locational") %>% distinct(genesymbol, parent, consensus_score) %>% filter(parent == "intracellular") %>% rename(score_intracellular = consensus_score) %>% group_by(genesymbol) %>% top_n(1, score_intracellular) %>% ungroup() %>% select(-parent) %>% distinct() 
other_location_score_df = all_annotations %>% filter(genesymbol %in% c(possible_ligands, possible_receptors) & aspect == "locational") %>% distinct(genesymbol, parent, consensus_score) %>% filter(parent != "intracellular") %>% rename(score_other = consensus_score) %>% group_by(genesymbol) %>% top_n(1, score_other)  %>% ungroup() %>% select(-parent) %>% distinct()

location_ligand_df = intracellular_score_df %>% full_join(other_location_score_df) 

location_ligand_df = location_ligand_df %>% 
  mutate_cond(is.na(score_intracellular), score_intracellular = 0) %>% 
  mutate_cond(is.na(score_other), score_other = 0) 
location_ligand_df = location_ligand_df %>% drop_na() %>% filter(score_intracellular > 0 | score_other > 0)

intracellular_ligands = location_ligand_df %>% filter(score_intracellular  >= (score_other) ) %>% pull(genesymbol) %>% intersect(possible_ligands) %>% sort() # many shit is removed indeed
intracellular_receptors = location_ligand_df %>% filter(score_intracellular  >= (score_other) ) %>% pull(genesymbol) %>% intersect(possible_receptors) %>% sort()# many shit is removed indeed
intracellular_ligands # ARF1, IRF8, MYH9, SOCS2
# "FGF11"          "FGF12"          "FGF14": not-shit?
possible_ligands_no_intracellular = possible_ligands %>% setdiff(intracellular_ligands) %>% setdiff(intracellular_receptors) %>% sort()
possible_receptors_no_intracellular = possible_receptors %>% setdiff(intracellular_receptors) %>% setdiff(intracellular_ligands) %>% sort()

#### step1D:  add the GO intercell ligand active to the set of ligands
all_annotations = import_omnipath_intercell()
GO_intercell_ligands =  all_annotations %>% filter(database == "GO_Intercell" & category == "ligand") %>% pull(genesymbol) %>% sort() ## to add to the list of ligands later on! The ones that are here, but also intracellular: give more importance to this!
GO_intercell_ligands %>% setdiff(possible_ligands_no_intracellular)
possible_ligands_no_intracellular = possible_ligands_no_intracellular %>% union(GO_intercell_ligands)

# useful analysis: compare with old nichenet ligands
# lr_network_nichenet = readRDS(url("https://zenodo.org/record/3260758/files/lr_network.rds")) # [beigelk] removing this so I can use my modified NicheNet model
# lr_network_nichenet = lr_network_nichenet %>% convert_alias2symbols_network_human(geneinfo_human) # [beigelk] removing this so I can use my modified NicheNet model
lr_network_nichenet = lr_network
nichenet_only_ligands = lr_network_nichenet$from %>% setdiff(possible_ligands_no_intracellular) %>% setdiff(possible_receptors_no_intracellular)  %>% unique() %>% sort() 
nichenet_only_receptors = lr_network_nichenet$to %>% setdiff(possible_receptors_no_intracellular) %>% setdiff(possible_ligands_no_intracellular)  %>% unique() %>% sort() 

nichenet_only_ligands # all the bad ones!: very good we were able to filter them out!

# useful analysis: compare with "problematic" ligands for which annotations and interactions were not always present or correct without the filtering steps described above
ligands_test = c("IFNA1", "CXCL16","TIGIT","NECTIN2", "PVR","NECTIN4", "CD226", "NOTCH1","IL4R","FYK","FYN","YBX1","HMGB1","HMGB2","LGALS1","NAMPT","FGF12","FGF14", "FGF11","CCN3","YARS","YARS1", "CXCR6")

possible_ligands_no_intracellular %>% intersect(ligands_test)
possible_receptors_no_intracellular %>% intersect(ligands_test)

intracellular_ligands %>% intersect(ligands_test)
intracellular_receptors  %>% intersect(ligands_test)

######################################################################################################################################################

### Step 2: Query Omnipath interactions for interactions between defined ligands and receptors

######################################################################################################################################################

#### ## ## ## ## ## ##  Get the Omnipath interaction network
all_omnipath = import_omnipath_interactions(
  resources = NULL,
  organism = 9606,
  datasets = c("omnipath","ligrecextra","pathwayextra"),
  fields = NULL,
  default_fields = TRUE,
  references_by_resource = TRUE,
  exclude = "Wang"
)

## Find interactions with a complex as at least one of the partners -- decomplixfy later
all_omnipath_complex =  all_omnipath %>% mutate(complex = grepl("COMPLEX",target)) %>% filter(complex == TRUE) 

all_omnipath_complex = seq(nrow(all_omnipath_complex)) %>% lapply(function(row_id, all_omnipath_complex){
  row = all_omnipath_complex[row_id,]
  targets = row$target_genesymbol %>% stringr::str_split("_") %>% unlist()
  tbl_targets = tibble(target_genesymbol = targets, target = row$target)
  colnames_order = colnames(row)
  row = row %>% select(-target_genesymbol) %>% inner_join(tbl_targets, by = "target") %>% select(colnames_order)
  return(row)
},all_omnipath_complex) %>% bind_rows(all_omnipath_complex) 

all_omnipath = all_omnipath %>% bind_rows(all_omnipath_complex %>% select(-complex)) 

```

# ####################################################################################################################################################
# ####################################################################################################################################################
# ####################################################################################################################################################

# ################################ !!!!!!!!!!!!!!!!!!!! END OF CODE FROM NICHENET !!!!!!!!!!!!!!!!!!!! ###############################################



# Table of OmniPath info for LR interactions of interest (wide)

Write this as a table.

```{r Write table to file}

#### ## ## ## ## ## ##  Query the Omnipath interaction network or ligands and receptors

# Original code from NciheNet had this:
# all_omnipath_lr = all_omnipath %>% filter(source_genesymbol %in% possible_ligands_no_intracellular & target_genesymbol %in% possible_receptors_no_intracellular) %>% distinct(source_genesymbol, target_genesymbol, curation_effort, sources) %>% group_by(source_genesymbol, target_genesymbol) %>% top_n(1, curation_effort) %>% ungroup() ## I think this will be a good lr network

# I (beigelk) have modified it to this in order to keep the sources in the full table:
all_omnipath_lr = all_omnipath %>% filter(source_genesymbol %in% possible_ligands_no_intracellular & target_genesymbol %in% possible_receptors_no_intracellular)

nichenet_sources = all_omnipath_lr %>%
  filter(source_genesymbol %in% nichenet_refs$from) %>%
  filter(target_genesymbol %in% nichenet_refs$to)

# write.table(
#   nichenet_sources,
#   file = paste0(proj_long, "/sankey_inferredLT/", proj_long, "_LR-DataSources_OmniPath_Top1to20-ligands-byLog2FC_all-LRlinks_all-LTlinks_Table_InferredLTPaths_V4.csv"),
#   row.names = FALSE, quote = FALSE, sep = "\t"
# )

fwrite(
  nichenet_sources,
  file = paste0(proj_long, "/sankey_inferredLT/", proj_long, "_LR-DataSources_OmniPath_", top_gene_lab, "-ligands_V4.tsv"),
  row.names = FALSE, quote = FALSE, sep = "\t"
)
```

#################

# Table of databases for receptor-target interactions

```{r}

receptor_target_sig = interactions_oi %>%
  dplyr::select(-c('cell_type')) %>%
  distinct(from, to, .keep_all = FALSE) %>%
  left_join(lr_network, relationship = "one-to-many") %>%
  dplyr::filter(is.na(database)) %>%
  dplyr::select(from, to) %>%
  left_join(sig_network, by = join_by(from, to), relationship = "one-to-many")

receptor_target_gr = receptor_target_sig %>%
  dplyr::filter(is.na(database)) %>%
  dplyr::select(from, to) %>%
  left_join(gr_network, by = join_by(from, to), relationship = "one-to-many")

receptor_target_refs = bind_rows(
  receptor_target_sig %>% dplyr::filter(!is.na(database)),
  receptor_target_gr
  )

# write.table(
#   receptor_target_refs,
#   file = paste0(proj_long, "/sankey_inferredLT/", proj_long, "_RT-DataSources_Top1to10-ligands-byLog2FC_all-LRlinks_all-LTlinks_Table_InferredLTPaths_V4.csv"),
#   row.names = FALSE, quote = FALSE, sep = ","
# )

fwrite(
  receptor_target_refs,
  file = paste0(proj_long, "/sankey_inferredLT/", proj_long, "_RT-DataSources_", top_gene_lab, "-ligands_V4.csv"),
  row.names = FALSE, quote = FALSE, sep = ","
)
```
